Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques

### 2018-02-12 paper/gloaguenJASMarticle.tex
bibliographie checked

This database is divided into two categories: $i)$ the \textit{event} category, which are the brief sounds (from 1 to 20 seconds) that are considered as salient including 245 sound event samples divided in 19 sound classes (\textit{ringing bell, whistling bird, sweeping broom, car horn, passing car, hammer, drill, coughing, barking dog, rolling suitcase, closing door, plane, siren, footstep, storm, street noise, metallic noise, train, tramway, truck and voice}) and $ii)$ the \textit{background} or \textit{texture} category that includes all the sounds that are of long duration and whose acoustic properties do not vary with respect to time. 154 sound samples that belong to this category are divided in 9 sound classes (\textit{whistling bird, construction site noise, crowd noise, park, rain, children playing in schoolyard, constant traffic noise, ventilation, wind}). These sounds are in .wav format sampled at 44.1 kHz. The sound class \textit{passing car} comes from 60 recordings of 2 cars (Renault Megane and Renault Scenic) made on the Ifsttar's runway at different speeds with multiple gear ratio. The other audio files have been found online (\textit{freesound.org}) and within the \textit{UrbanSound8k} database \cite{salamon_dataset_nodate}. Each sound class is composed of multiples samples (\textit{bird01.wav}, \textit{bird02.wav} \dots) to allow some diversity in the resulting mixture, see Figure \ref{fig:example_simScene}. The software allows the user to control some high level parameters (number of events of each class that appear in the mixture, elapsed time between each sample of a same class, presence of a fade in and a fade out \dots) completed with a standard deviation that may bring some random behavior between the scenes. Furthermore, an audio file of each sound class present in the scene can be generated that allows us to know its exact contribution as well as a text file that summarizes the time presence of all the events.\\

>>>>

This database is divided into two categories: $i)$ the \textit{event} category, which are the brief sounds (from 1 to 20 seconds) that are considered as salient including 245 sound event samples divided in 19 sound classes (\textit{ringing bell, whistling bird, sweeping broom, car horn, passing car, hammer, drill, coughing, barking dog, rolling suitcase, closing door, plane, siren, footstep, storm, street noise, metallic noise, train, tramway, truck and voice}) and $ii)$ the \textit{background} or \textit{texture} category that includes all the sounds that are of long duration and whose acoustic properties do not vary with respect to time. 154 sound samples that belong to this category are divided in 9 sound classes (\textit{whistling bird, construction site noise, crowd noise, park, rain, children playing in schoolyard, constant traffic noise, ventilation, wind}). These sounds are in .wav format sampled at 44.1 kHz. The sound class \textit{passing car} comes from 60 recordings of 2 cars (Renault Megane and Renault Scenic) made on the Ifsttar's runway at different speeds with multiple gear ratios. The other audio files have been found online (\textit{freesound.org}) and within the \textit{salamon2014dataset} database \cite{salamon_dataset_nodate}. Each sound class is composed of multiples samples (\textit{bird01.wav}, \textit{bird02.wav} \dots) to allow some diversity in the resulting mixture, see Figure \ref{fig:example_simScene}. The software allows the user to control some high level parameters (number of events of each class that appear in the mixture, elapsed time between each sample of a same class, presence of a fade in and a fade out \dots) completed with a standard deviation that may bring some random behavior between the scenes. Furthermore, an audio file of each sound class present in the scene can be generated that allows us to know its exact contribution as well as a text file that summarizes the time presence of all the events.\\
